Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-08-09 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Corrections
Corrections from Ravi

A general theory for the conductivity of a dressed system with the disorder averaging was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}. Within this theory, the general $x$-directional longitudinal DC-limit conductivity has been discribed by
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are the $x$-directional electric current operator matrix elements' $0$-th Fourier component and the white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considering two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2}.
\end{equation}
Here, $ \varepsilon_N$ are quasienergies of all considering Floquet states, and $tr[\cdot]$ is the trace of the considering operator.

@@

Eq.~(\ref{eq_20}) can be expanded using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} \equiv \ket{n,k_x}$

@@

We can diagonalize the impurity averaged Green's functions using a unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) as mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}. Thus, we evaluate the matrix element of the difference between retarded and advanced Green's functions as

@@

expressions form Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we obtain

@@

Since the inverse scattering time matrix being equal to the diagonalized contrast of the retarded and advanced self-energy, and on the diagonal the contrast of the retarded and advanced Green's function can be represented with the imaginary component of the retarded self-energy \cite{wackerl20,wackerlthesis20}, we can identify the following property

@@

However, by considering the condition that the center of the cyclotron orbit $y_0$ must physically lie within the considering system $-L_y/2 < y_0 < L_y/2$, we can identify that

@@

where $k_B$ is theBoltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system. Considering the above distribution with extremely low temperature conditions, we use thee following approximation

@@

  - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F),

@@

and by letting $\Pi = \varepsilon_F$, the derived expression in \ref{eq_29} leads to

>>>>

A general theory for the conductivity of a dressed system with the disorder averaging was reported by Wackerl \textit{et al.} \cite{wackerl20,wackerlthesis20}. This theory, the general $x$-directional longitudinal DC-limit conductivity has been characterized as
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are the $x$-directional electric current operator matrix elements' $0$-th Fourier component and the white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $0$-th Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considered two-dimensional system, $f$ is the partial distribution function, and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2}.
\end{equation}
Here $ \varepsilon_N$ are quasienergies of all relevant Floquet states, and $tr[\cdot]$ is the trace of the considering operator.

@@

Eq.~(\ref{eq_20}) can be expanded using only the central entry Fourier components ($l=l'=0$) of Floquet modes $\ket{\phi_{n,m}} \equiv \ket{n,k_x}$ as

@@

We can diagonalize the impurity averaged Green's functions using a unitary transformation ($\vb{T}  \equiv \ket{n,k_x}$) as mentioned in Refs.~\cite{wackerl20,wackerlthesis20,tsuji08}. Thus, we evaluate the matrix elements of the difference between retarded and advanced Green's functions as

@@

expressions from Eq.~(\ref{eq_24}) and Eq.~(\ref{eq_25}) back into Eq.~(\ref{eq_23}) we obtain

@@

The inverse scattering time matrix is equal to the diagonalized contrast of the retarded and advanced self-energy \cite{wackerl20,wackerlthesis20}. In addition, on the diagonal the contrast of the retarded and advanced Green's function can be represented with the imaginary component of the retarded self-energy \cite{wackerl20,wackerlthesis20}. Subsequenty, we can identify the following property

@@

However, by considering the condition that the center of the cyclotron orbit $y_0$ must physically lie within the considered system, we can identify that

@@

where $k_B$ is theBoltzmann constant, $T$ is the absolute temperature and $\varepsilon_F$ is the Fermi energy of the system. Considering the above distribution for extremely low temperature conditions, we can use the following approximation

@@

  - \pdv{f(\varepsilon)}{\varepsilon} \approx \delta(\varepsilon - \varepsilon_F).

@@

Moreover, let $\Pi = \varepsilon_F$ and the derived expression in \ref{eq_29} leads to

### 2021-08-09 paper/v1.0/sections/6_manipulate_conductivity.tex
Corrections from Ravi

To identify the characteristics of the longitudinal conductivity of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
Here we derive a normalized $x$-directional conductivity of dressed quantum Hall system using the natural conductivity of the least Landau level
\begin{equation} \label{eq_35}
  \begin{aligned}
    \tilde{\sigma}^{xx} =
    \sigma_{0} &
    \sum_{n}
    \frac{\qty(n+1)}{0.0037\Lambda_n \Lambda_{n+1}} \\
    & \times
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{0.06\Lambda_n})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{0.06\Lambda_{n+1}})^2
      }
    ],
  \end{aligned}
\end{equation}
with $\sigma^0 = e^2/\pi \hbar A$.

We use this expression to illustrate the changes that can be done to the longitudinal conductivity of 2DEG under stationary magnetic field using an external dressing field. As given in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considering system.
For a given dressing field intensity, the longitudinal conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values.
In quantum Hall systems, electrons are restricted to bear only the Landau level energies. Thus, the conductivity gets very low values when the Fermi level is not aligned with any of the Landau level energy values. In contrast, on each Landau level, the conductivity achieve excessive values compared to other areas. Moreover, as illustrates in Fig.~\ref{fig_5} the peak value of the normalized longitudinal conductivity on each Landau level gets increase with the Landau level number.

@@

On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field shrink the conductivity regions near Landau levels.
When we increase the intensity level of the dressing field, the conductivity regions get more weaken as illustrate in the \ref{fig_6}.
However, the peak value of the conductivity at each Landau level has the same value as the undressed system. This demonstrates that we are able to tune the width of the regions of conductivity in these quantum Hall systems with the help of a dressing field.

These characteristics are aligned with the results demonstrated by Dini \textit{et al.} \cite{dini16} and as they remarked since the Fermi level of the system can be changed with the applied gate voltage of the material this can be utilized as a 2D switch for nanoscale optoelectronics applications. Controlling  the external dressing field's intensity, we are able to fine-tune this switching mechanism for an optimized performance.
Furthermore, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_5} and \ref{fig_6} are generally incompatible with the results reported in Ref.~\cite{dini16}. This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}. The semi-elliptical conductivity regions illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed Landau levels representation \cite{endo09}.
In our study of the transport properties of quantum Hall systems, we developed the conductivity expression starting from the Floquet-Drude conductivity \cite{wackerl20} and we achieved outcomes that align with the result depicted in Ref. \cite{endo09}.
The theory on the conductivity of quantum Hall systems in Ref.~\cite{endo09} provides an excellent agreement with the experimently observed results in GaAs/AlGaAs 2DEG for the low magnetic field range.
However, they have not considered the tunability that can be achieved with a dressing field. In this analysis, we account both of the magnetic and dressing field effects that can be applied to the transport properties of 2DEG, and we have presented a more generalized theory. As a concluding remark, in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more experimental fitting and generalized mathematical model for the charge transport properties of quantum Hall systems.

>>>>

To identify the longtitudinal conductivity characteristics of quantum Hall system under external dressing field, first we derive an expression for normalized longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$.
Here we derive a normalized $x$-directional conductivity of dressed quantum Hall system using the natural conductivity of the least Landau level
\begin{equation} \label{eq_35}
  \begin{aligned}
    \tilde{\sigma}^{xx} =
    \sigma_{0} &
    \sum_{n}
    \frac{\qty(n+1)}{0.0037\Lambda_n \Lambda_{n+1}} \\
    & \times
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{0.06\Lambda_n})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{0.06\Lambda_{n+1}})^2
      }
    ],
  \end{aligned}
\end{equation}
with $\sigma^0 = e^2/\pi \hbar A$.

As illustrated in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the normalized longitudinal conductivity $\tilde{\sigma}^{xx}$ with the applied dressing field's intensity and the Fermi level $X_F$ of the considering system.
For a given dressing field intensity, the longitudinal conductivity vary with  the Fermi level of the system showing sharp peaks at each Landau energy level.
In quantum Hall systems, electrons are restricted to bear only the Landau energies. Thus, the conductivity reduces significantly when the Fermi level is not aligned with any of the Landau levels. In contrast, near each Landau level, the conductivity achieve excessive values compared to other areas. Moreover, as illustrates in Fig.~\ref{fig_5} the peak value of the normalized longitudinal conductivity on each Landau level gets increase with the Landau level number.

@@

On the other hand, considering the effects of the applied dressing field on the longitudinal conductivity of 2DEG, we can identify that the dressing field has sharpen the conductivity peaks.
When we increase the intensity level of the dressing field, the conductivity regions get more weaken as illustrate in the \ref{fig_6}.
However, the peak value of the conductivity at each Landau level has the same value as the undressed system. This demonstrates our ability to tune the width of the conductivity regions in these quantum Hall systems with the help of a dressing field.

These characteristics align well with the outcomes demonstrated by Dini \textit{et al.} \cite{dini16}.  As the authors remarked in that work, since the Fermi level of the system can be changed with the applied gate voltage of the material this can be utilized as a 2D switch for nanoscale optoelectronics applications. Controlling  the external dressing field's intensity, allows us to fine-tune this switching mechanism for an optimized performance.
However, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_5} and \ref{fig_6} are generally incompatible with the results reported in Ref.~\cite{dini16}. This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}. The semi-elliptical conductivity regions illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed data for Landau levels \cite{endo09}.
In our study of the transport properties of quantum Hall systems, we developed the conductivity expression starting from the Floquet-Drude conductivity \cite{wackerl20} and we achieved outcomes that align with the results depicted in Ref. \cite{endo09}.
The theory on the conductivity of quantum Hall systems in Ref.~\cite{endo09} provides an excellent agreement with the experimently observed results in GaAs/AlGaAs 2DEG for the low magnetic field range.
However, they have not considered the tunability that can be achieved with a dressing field. In this analysis, we account both of the magnetic and dressing field effects that can affect the transport properties of 2DEG, leading to a more generalized theory. Thus in this study, we were able to demonstrate that using Floquet-Drude conductivity method, one can derive a more generalized mathematical model which fits better with experiment for the charge transport properties of quantum Hall systems.

### 2021-08-09 paper/v1.0/sections/7_conclusions.tex
Corrections from Ravi

In this analysis, we introduced a generalized mathematical model for charge transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light. Under the uniform magnetic field, the charged particles can only settle in discrete energy values and this leads to the Landau quantization. We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method. We assumed the impurities in the material as a Gaussian random scattering potential. Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.

Our derived analytical expressions disclosed that the transport characteristics of the dressed quantum Hall system can be controlled by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
We found that the graphical illustrations that we obtained from these numerical calculatiuons are capable of producing the same behavior as the experimental  result found in undressed quantum Hall systems.
Furthermore, we identified that by increasing the intensity of the radiation, the conductivity regions near the Landau levels can be squeezed. Despite, this behavior has been identified in previous works, their results are not coinciding with the more accurate description of conductivity components in undressed quantum Hall systems. However, our generalized analysis on conductivity of dressed quantum Hall systems provide a well-suited description for these specific quantum Hall systems.

In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties of dressed quantum Hall systems. Moreover, our detailed theoretical analysis showed that the recently introduced Floquet-Drude conductivity model can be adopted to extend the models that were used to describe the transport characteristics in quantum Hall systems. Due to owing the ability to control the conductivity regions, high intensity external illumination can be used as a trigger for two-dimensional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices. Finally, we identified that our findings of this paper can be used towards understanding nanoscale quantum devices, enhancing their performance, and inventing novel appliances.

>>>>

In this paper, we introduced a generalized mathematical model for prediciting  charge transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light. Under the uniform magnetic field, the charged particles can only settle in discrete energy values which leads to the Landau quantization. We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method. We assumed the impurities in the material as a Gaussian random scattering potential. Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.

Our derived analytical expressions disclosed that the transport characteristics of the dressed quantum Hall system can be controlled by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field.
We found that the graphical illustrations that we obtained from these numerical calculatiuons are capable of producing the same behavior as experiments on quantum Hall systems in the absence of a dressing field.
Furthermore, we identified that by increasing the intensity of the radiation, the conductivity regions near the Landau levels can be squeezed. Despite this behavior being identified in previous works, their results did not coincide with the more accurate description of conductivity components in undressed quantum Hall systems. However, our generalized analysis on conductivity of dressed quantum Hall systems provide a well-suited description for these specific quantum Hall systems.

In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties of dressed quantum Hall systems. Moreover, our detailed theoretical analysis showed that the recently introduced Floquet-Drude conductivity model can be adopted to extend the models that were used to describe the transport characteristics in quantum Hall systems. Owing the ability to control the conductivity regions, high intensity external illumination may be used as a trigger for two-dimensional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices. As a concluding remark, we believe that our findings of this paper can be used towards understanding the 2D opto-electronic nano transistors, enhancing their performance, and inventing novel appliances.
